### 2010-11-05 docs/tex/mimicry.tex
Updates on proof reading.
Mimicry chapter updated

@@

>>>>

\begin{quote}
``It is not the strongest of the species that survives, nor the most intelligent that survives. It is the one that is the most adaptable to change. - Charles Darwin"
\end{quote}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=1]{images/Batesplate_ArM}
	\caption{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
	\label{fig:plot-2-prey}
\end{figure}

\subsection{Definitions of Mimicry}
The definition of mimicry provided by Bates is quite restricted and is similar to the following

\begin{quote}
``resemblance in external appearance, shapes and colours between members of widely distinct families."
\end{quote}

The following more sophisticated definition was provided at the international Zoological Congress in Washington, 1963,

\begin{quote}
``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."
\end{quote}

The best known defintion of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}. The clauses are presented in the following:

\begin{itemize}
	\item ``that the imitative species occur in the same area and occupy the same station as the immitated". This increases the probability that a predator will affect both parties concerned. Neverthless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
	\item ``that the imitators are always the more defenceless". It will be seen later on in the discussion of Mertensian mimicry among coral snakes that the more offensive party may occasionally be the mimic. 
	\item ``that the imitators are always less numerous in individuals". What is meant here is that the deceived animal should encounter the mimic less often than the model. This is true when the deceived animal must learn to recognize model and mimic and when positive and negetive experiences carry equal weight. But it is known from various learning experiments that when an animal has learn about warning coloration, negetive experiences or punishment stimuli (such as iedibility) can have a stronger and more lasting effect than positive experiences. Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces. When the deceptive animal possesses an innate reaction to the model the number of mimics can be virtually unlimited. 
	\item ``that the imitators differ from the bulk of their allies". When this condition applies, our attention is of course most easily attracted. The most remarkable cases of mimicry are those where close relatives form divergent models. It is neverthless highly possible that groups of closely related species may be similar mimics of the same model. Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry. 
	\item ``that the imitation, however minute, is external and visible only, never extending to internal charecters or to such as do not affect the external appearance." This criteria, like the previous one is aimed at defining mimmicry as a special adaptation. But if one of two closely related species both of which are posinous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
\end{itemize}

These five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed. But such supplementary clauses cannot be used as a definition of mimicry in general, though this is unfortunately often attempted.

### 2010-11-05 docs/tex/model.tex
Mimicry chapter updated

\begin{quotation}
``Modeling, it should be clear is an art form. It depends on the experience and taste of the modeler. In this it is much like cartooning. The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" \cite{holland1996}.
\end{quotation}

>>>>

\begin{quotation}
``Modeling, it should be clear is an art form. It depends on the experience and taste of the modeler. In this it is much like cartooning. The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point) - John H. Holland" \cite{holland1996}.
\end{quotation}
